The Impact of ChatGPT news on MSFT

### 2023-12-02 MSFT.Rmd
included GARCH and dummy ChatGPT code

```{r echo=FALSE, include=TRUE}
if (!require("vars")) install.packages("vars", dependencies=TRUE)
if (!require("tseries")) install.packages("tseries", dependencies=TRUE)
if (!require("quantmod")) install.packages("quantmod", dependencies=TRUE)

library(vars)
library(tseries)
library(quantmod)

@@

ChatGPT <- read.csv("ChatGPT.csv")

@@

```{r echo=FALSE, include=TRUE}
MSFT_returns <- na.omit(diff(log(MSFT)))
adf.test(MSFT_returns)

@@

```{r echo=FALSE, include=TRUE}
coeftest(VAR_est)
MSFT_VAR <- VAR(cbind(MSFT_returns, ChatGPT), ic="AIC", lag.max = 24)

@@

```{r echo=FALSE, include=TRUE}
causality(MSFT_VAR, cause="ChatGPT")["Granger"] 
causality(VAR_est, cause="Inflation_CH")["Granger"]

@@

```{r echo=FALSE, include=TRUE}
plot(irf(VAR_est, impulse="ChatGPT", response="MSFT_returns"))

@@

>>>>

```{r echo=FALSE, include=TRUE}
if (!require("vars")) install.packages("vars", dependencies=TRUE)
if (!require("tseries")) install.packages("tseries", dependencies=TRUE)
if (!require("quantmod")) install.packages("quantmod", dependencies=TRUE)
if (!require("PerformanceAnalytics")) install.packages("PerformanceAnalytics", dependencies=TRUE)
if (!require("forecast")) install.packages("forecast", dependencies=TRUE)
if (!require("rugarch")) install.packages("rugarch", dependencies=TRUE)

library(PerformanceAnalytics)
library(forecast)
library(rugarch)
library(vars)
library(tseries)
library(quantmod)

@@

#ChatGPT <- read.csv("ChatGPT.csv")

@@

```{r echo=FALSE, include=TRUE}
MSFT_returns <- na.omit(diff(log(MSFT)))
colnames(MSFT_returns)<-"MSFT_Returns"
adf.test(MSFT_returns)

@@

```{r echo=FALSE, include=TRUE}
coeftest(VAR_est)
#MSFT_VAR <- VAR(cbind(MSFT_returns, ChatGPT), ic="AIC", lag.max = 24)

@@

```{r echo=FALSE, include=TRUE}
#causality(MSFT_VAR, cause="ChatGPT")["Granger"] 
#causality(VAR_est, cause="Inflation_CH")["Granger"]

@@

```{r echo=FALSE, include=TRUE}
#plot(irf(VAR_est, impulse="ChatGPT", response="MSFT_returns"))

@@

GARCH Model:

For our GARCH model we calculate a 30-day rolling volatility

```{r echo=FALSE, include=TRUE}
chart.RollingPerformance(R = MSFT_returns, width = 30,
                         FUN = "sd.annualized", scale = 252, main = "30-day rolling volatility")

```
To setup a GARCH Model for our MSFT analysis we have to specify the orders of an ARMA model as well as a GARCH Model.

From class we learned, that in Finance is it common to stick to a GARCH(1,1) model, so we just need to estimate the ARMA model orders. For this, we let auto.arima find the best fitting orders

```{r echo=FALSE, include=TRUE}
auto.arima(MSFT_returns)
```

We see that auto.arima has found that the auto-regressive (AR) part of the ARMA model has an order of 2 present as the coefficients ar1 and ar2 were estimated. The Absence of ma coefficients suggests that the Moving Average (MA) part has an order of 0.

Now we can specify our GARCH model and fit it to our data.

```{r echo=TRUE, include=TRUE}
MSFT_garch_spec <- ugarchspec(mean.model = list(armaOrder = c(2,0), include.mean = TRUE),
                        variance.model = list(garchOrder = c(1,1), model = "sGARCH"))

MSFT_garch_fit <- ugarchfit(data = MSFT_returns, spec = MSFT_garch_spec)
```

Now we can use the sigma method to extract the estimated GARCH volatilities, so that we can plot them on a chart

```{r echo=FALSE, include=TRUE}
MSFT_volatility <- sigma(MSFT_garch_fit)

par(mfrow=c(2,1)) 
plot(MSFT_volatility, main="MSFT GARCH volatility")
plot(abs(MSFT_returns), main="Realized volatility")
```

AS a last step, we may forecast the returns and volatility values.
Here, ARMA will estimate the returns, while GARCH estimates the volatilities

```{r echo=FALSE, include=TRUE}
par(mfrow=c(1,1))
MSFT_volatility_forecast <- ugarchforecast(fitORspec = MSFT_garch_fit, n.ahead = 5)
plot(MSFT_volatility_forecast, which=1)
plot(MSFT_volatility_forecast, which=3)
```

```{r echo=FALSE, include=TRUE}
auto.arima(MSFT_returns)
```

```{r echo=FALSE, include=TRUE}
auto.arima(MSFT_returns)
```

```{r echo=FALSE, include=TRUE}
auto.arima(MSFT_returns)
```
